### 2016-04-03 ch04-lrmhinf/ch04appendices.inc.tex
Some small things

\begin{figure}
\setlength\figurewidth{\columnwidth}
  \includegraphics[width=\figurewidth]{\thisDir/figs/simulink-setup.pdf}
  \caption{Simulink model used during the AVIS measurements. All signals are six-dimensional real values.}
  \label{fig:avis:simulink:setup}
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics{\thisDir/figs/avis-with-axes.pdf}
  \caption{\glsentrytext{AVIS} with $(x,y,z)$ coordinate frame indicated and bird's eye view of the approximate locations of the actuators and sensors at each of the four corners. For each of the actuators and sensors, the color indicates the principal direction.}
  \label{fig:avis:withAxes}
\end{figure}

@@

\begin{figure}[p]
\setlength\figurewidth{0.75\columnwidth}
\setlength\figureheight{0.68\figurewidth}
\input{\thisDir/figs/avis-setup-filters.tikz}
\caption{Bode plots of the elements of $\experimental\Controller$ and sensor filter $F$ present in the set-up.}
\label{fig:avis:bodeplots:controllerAndSensor}
\end{figure}

@@

\begin{figure}[p]
\setlength\figurewidth{\columnwidth}
  \includegraphics[width=\figurewidth]{\thisDir/figs/simulink-avis.pdf}
  \caption{Simulink model of the AVIS sub-block.}
  \label{fig:avis:simulink:avis}
\end{figure}

>>>>

\begin{figure}
\setlength\figurewidth{\columnwidth}
  \includegraphics[width=\figurewidth]{\thisDir/figs/simulink-setup.pdf}
  \caption[\Simulink model used on the \glsentryshort{AVIS}]{\Simulink model used during the AVIS measurements. All signals are six-dimensional real values.}
  \label{fig:avis:simulink:setup}
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics{\thisDir/figs/avis-with-axes.pdf}
  \caption[\glsentryshort{AVIS} with coordinate frame, sensors and actuators.]{\glsentrytext{AVIS} with $(x,y,z)$ coordinate frame indicated and bird's eye view of the approximate locations of the actuators and sensors at each of the four corners. For each of the actuators and sensors, the color indicates the principal direction.}
  \label{fig:avis:withAxes}
\end{figure}

@@

\begin{figure}[p]
\setlength\figurewidth{0.75\columnwidth}
\setlength\figureheight{0.68\figurewidth}
\input{\thisDir/figs/avis-setup-filters.tikz}
\caption[\glsentryshort{AVIS} controller and filters]{Bode plots of the elements of $\experimental\Controller$ and sensor filter $F$ present in the set-up.}
\label{fig:avis:bodeplots:controllerAndSensor}
\end{figure}

@@

\begin{figure}[p]
\setlength\figurewidth{\columnwidth}
  \includegraphics[width=\figurewidth]{\thisDir/figs/simulink-avis.pdf}
  \caption{\Simulink model of the \glsentryshort{AVIS} sub-block.}
  \label{fig:avis:simulink:avis}
\end{figure}

### 2016-04-03 config/glossaries.inc.tex
Address some minor TODOs
Lots of work on LRMHinf + description of AVIS setup
Lots of changes to CH04
Some small things

\newsymbolglos{B-imagunit}{j}{The imaginary unit, $j = \sqrt{-1}$}
\newsymbolglos{B-epsilon}{\eps}{The numerical precision of a floating point number (\code{eps}), e.g. $\eps \approx 2.2 \cdot 10^{-16}$ for \code{double} precision}

@@

\newsymbolglos{operator-cardinality}{\numberOf \placeholder}{Number of elements (cardinality) in the set \placeholder}
\newsymbolglos{operator-exp}{\expval{\placeholder}}{Expected value of \placeholder}
\newsymbolglos{operator-ln}{\ln \placeholder}{Natural logarithm of \placeholder}
\newsymbolglos{operator-conj}{\conj \placeholder}{Complex conjugate of \placeholder}
\newsymbolglos{operator-log}{\log_{B} \placeholder}{Logarithm in base $B$ of \placeholder{}  (when $B$ is omitted, $B=10$ is implied)}
\newsymbolglos{operator-matrix-ht}{\placeholder^{\HT}}{Hermitian (complex conjugated) transpose of the matrix \placeholder}
\newsymbolglos{operator-matrix-pinv}{\pinv{\placeholder}}{Moore-Penrose pseudo-inverse of the matrix \placeholder}
\newsymbolglos{operator-matrix-tran}{\placeholder^{\TT}}{Transpose of the matrix \placeholder}
\newsymbolglos{operator-round-ceil}{\ceil{\placeholder}}{\placeholder{} rounded upwards (\code{ceil})}
\newsymbolglos{operator-round-floor}{\floor{\placeholder}}{\placeholder{} rounded downwards (\code{floor})}
\newsymbolglos{operator-round-round}{\round{\placeholder}}{\placeholder{} rounded towards the nearest integer, as in \glsentrytext{IEEE} 754-2008 (\code{round})}

\newsymbolglos{sys-damping}{\damping}{Relative damping of a system}
\newsymbolglos{sys-resonance}{\wn}{Natural (resonance) frequency of a system}
\newsymbolglos{sys-timeconst}{\tau}{Time constant of a system}

@@

\newacronym{DAC}{DAC}{digital-to-analog converter}
\newacronym{DC}{DC}{direct current (also: mean value)}
\newacronym{DCkernel}{DC kernel}{diagonal correlated kernel}
\newacronym{DFT}{DFT}{discrete Fourier transform}
\newacronym{DSA}{DSA}{dynamic signal analyzer}
\newacronym{DTFT}{DFT}{discrete-time Fourier transform}
\newacronym{DUT}{DUT}{device under test}

@@

\newacronym{PDF}{PDF}{probability distribution function}
\newacronym{PRESS}{PRESS}{prediction residual error sum of squares}
\newacronym{PSD}{PSD}{power spectral density}

>>>>

\newsymbolglos{B-imagunit}{j}{The imaginary unit, $j = \sqrt{-1}$}
% \newsymbolglos{B-epsilon}{\eps}{The numerical precision of a floating point number (\code{eps}), e.g. $\eps \approx 2.2 \cdot 10^{-16}$ for \code{double} precision}

@@

\newsymbolglos{operator-cardinality}{\numberOf \placeholder}{Number of elements (cardinality) in the set \placeholder}
\newsymbolglos{operator-exp}{\expval{\placeholder}}{Expected value of \placeholder}
\newsymbolglos{operator-ln}{\ln}{Natural logarithm}
\newsymbolglos{operator-conj}{\conj \placeholder}{Complex conjugate of \placeholder}
\newsymbolglos{operator-log}{\log_{B}}{Logarithm in base $B$ (when $B$ is omitted, $B=10$ is implied)}
\newsymbolglos{operator-matrix-ht}{\placeholder^{\HT}}{Hermitian (complex conjugated) transpose of the matrix \placeholder}
\newsymbolglos{operator-matrix-pinv}{\pinv{\placeholder}}{Moore-Penrose pseudo-inverse of the matrix \placeholder}
\newsymbolglos{operator-matrix-tran}{\placeholder^{\TT}}{Transpose of the matrix \placeholder}
\newsymbolglos{operator-matrix-conv}{\conv}{Convolution}
\newsymbolglos{operator-matrix-kron}{\kron}{Kronecker product of matrices (\code{kron})}
\newsymbolglos{operator-matrix-hadamard}{\hadamard}{Hadamard (element-wise) product of matrices (\code{.*})}
\newsymbolglos{operator-round-ceil}{\ceil{\placeholder}}{\placeholder{} rounded upwards (\code{ceil})}
\newsymbolglos{operator-round-floor}{\floor{\placeholder}}{\placeholder{} rounded downwards (\code{floor})}
\newsymbolglos{operator-round-round}{\round{\placeholder}}{\placeholder{} rounded towards the nearest integer, as in \glsentrytext{IEEE} 754-2008 (\code{round})}

\newsymbolglos{sys-damping}{\damping}{Relative damping of a pole or system}
\newsymbolglos{sys-resonance}{\wn}{Natural (resonance) frequency of a pole or system}
\newsymbolglos{sys-timeconst}{\timeconst}{Time constant of a pole or system ($\timeconst \isdef (\damping \wn)^{-1}$)}

@@

\newacronym{DAC}{DAC}{digital-to-analog converter}
\newacronym{DAQ}{DAQ}{data acquisition}
\newacronym{DC}{DC}{direct current (also: mean value)}
\newacronym{DCkernel}{DC kernel}{diagonal correlated kernel}
\newacronym{DFT}{DFT}{discrete Fourier transform}
\newacronym{DSA}{DSA}{dynamic signal analyzer}
\newacronym{DTFT}{DFT}{discrete-time Fourier transform}
\newacronym{DUT}{DUT}{device under test}

@@

\newacronym{PDF}{PDF}{probability distribution function}
\newacronym{PI}{PI}{proportional-integral}
\newacronym{PRESS}{PRESS}{prediction residual error sum of squares}
\newacronym{PSD}{PSD}{power spectral density}
